Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-24 paper/main.tex
gamma coloring and sheave/fiber rework

A fiber bundle has many sections, and the set of all sections
\begin{equation}
\label{eq:related-work:continuity:sections}
\{\dsectionc^{i}: \opensetc\rightarrow \dtotalc\}|_{i\in I} = \cgamma{\opensetc}{\dtotalc}
\end{equation}
over an open set $openset \subseteq \dtotal$ is the set of all data sets with a shared fiber \dfiber\ and continuity \dbase. The set of all sections defined over the total base space is denoted $\Gamma(\dbase, \dtotal)$.

\subsubsection{Sheaves}
Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf $\sheafc$ is a map from the open set to the set of sections $\sheafc: \opensetc \rightarrow \gammac{\openset}{ \dtotal}$ \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves inclusion maps $\iota$ between open sets and the inclusion map $\iota^*$ between the sets of sections.

@@

This means that a smaller space $\openset_1$ is included in a larger space $\openset_2$ and a function that is continuous over a larger space $\openset_2$ is continuous over a subspace $\openset_1 \subset\openset_2$. Sheaves are presheafs where sets of sections $\Gamma$ are defined over unions of open sets over a topology $\bigcup_{j \in I} \openset)_j \in \dtotal$ \cite{spanier1989algebraic, nlab:sheaf}. Sheaves provide a mathematical abstraction of data, the space it lives over, and relationships between subsets.

@@

\begin{definition} A category \mathcal{C} consists of a collection of objects $c$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    C_1 \arrow[r, "f"] \arrow[rd, "g\circ f"'] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145] & C_2 \arrow[d, "g"] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55] \\
  & C_3 \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

 \begin{definition} An opposite category $\mathcal{C}^{op}$ is a category with all the same objects of category $\mathcal{C}$ and but the morphisms are reversed. For example $f:C_1 \rightarrow C_2$ in $\mathcal{C}$ is $f:C_2 \rightarrow C_1$ in $\mathcal{C}^{op}$.   
 \end{definition}

@@

We model data as the sheaf $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op}\rightarrow \bm{Set}$. The objects of \textbf{Set} in this sheaf are the sets of sections introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps in \autoref{eq:related-work:continuity:presheaf}. 
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \Gamma(\opensetc_i, \dtotalc) \in Ob(\bm{Set}) & \\
{} \arrow[rr, "\dfuncc", Rightarrow, pos=.3, shorten <=3.5em, shorten >=8.85em] & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{op}) \arrow[uu, "\sheafc(\dtotalc)", bend left, shift left = 10.5] \arrow[uu, "\sheafc(\dtotalc)"', bend right, shift left=10.5] &   
\end{tikzcd}
\end{equation}
 The map $\dfunc: \sheaf(\dtotal) \rightarrow \sheaf(\dtotal)$ is any arbitrary function between sheafs. The sheaf $\sheaf(\dtotal)$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf(\dtotal)|_{\dbasepoint}\coloneqq \lim\limits_{\openset\ni \dbasepoint} \Gamma(\openset, \dtotal)$ \cite{StalkSheaf2019}.

@@

The fiber space over a point is embedded in the stalk over that point $\dfiber_{\dbasepoint}\hookrightarrow \mathscr{\dfiber}_{\dbasepoint}$. The sheaf maps \dfunc\ restricted to the stalk are members of $hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$. The maps $\dfunc \in Hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$ include the types of data transformations described in \autoref{sec:related-work:equivariance}. When a fiber bundle is trivial, we can dispense with localization and directly consider the fiber maps $Hom(\dfiber_{\dbasepoint}, \dfiber_{\dbasepoint})$ over a point \dbasepoint. In \autoref{sec:artist:construction}, we assume that the fiber bundles are trivial.

The continuity of the graphic is encapsulated as a category $\mathcal{\mathcal{\gbase}}$ containing open set objects $\opensetg$, the complete set of opensets $\gbase$ that is the full space of the graphic, and the empty set. As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
  \{\gsectionc^{i}:\opensetgc_i\rightarrow \gtotalc\}|_{i\in I}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}
    {Ob(\bm{Set}) \ni \Gamma(\opensetgc_i, \gtotalc)}                                                                                                  &  & \{\gsectionc^{j}:\opensetgc_i\rightarrow \gtotalc\}|_{j\in J} \arrow[ll, "\iota"', hook'] \\ &  & \\
    \opensetgc_i \arrow[uu, "\sheafc(\gtotalc)"] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheaf_{\vartist}(\gtotalc)" description, dashed] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset $\{\gsection^{j}\}|_{j\in J}$ of the full set of graphics. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf $\sheaf_{\vartist}$ from the graphic base space to the set of reachable graphics.

@@

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartist: \sheafc_{\vindex^*}(\dtotal) \rightarrow \sheafc_{\vartist}(\gtotal)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set.

>>>>

A fiber bundle has many sections, and the set of all sections over an open set $openset \subseteq \dtotal$
\begin{equation}
\label{eq:related-work:continuity:sections}
\cgamma{\opensetc}{\dtotalc} \coloneqq \{\dsectionc^{i}: \opensetc\rightarrow \dtotalc\}|_{i\in I}
\end{equation}
 is the set of all data sets with a shared fiber \dfiber\ and continuity \dbase. The set of all sections defined over the total base space is denoted $\Gamma(\dbase, \dtotal)$.

\subsubsection{Sheaves}
Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf $\sheafc$ is a map from the open set to the set of sections $\sheafc: \opensetc \rightarrow \cgamma{\openset}{ \dtotal}$ \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves inclusion maps $\iota$ between open sets and the inclusion map $\iota^*$ between the sets of sections.

@@

This means that a smaller space $\openset_1$ is included in a larger space $\openset_2$ and a function that is continuous over a larger space $\openset_2$ is continuous over a subspace $\openset_1 \subset\openset_2$. Sheaves are presheafs where sets of sections are defined over unions of open sets over a topology $\bigcup_{j \in I} \openset)_j \in \dtotal$ \cite{spanier1989algebraic, nlab:sheaf}. Sheaves provide a mathematical abstraction of data, the space it lives over, and relationships between subsets.

@@

\begin{definition} A category $\mathcal{C}$ consists of a collection of objects $c$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    C_1 \arrow[r, "f"] \arrow[rd, "g\circ f"'] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145] & C_2 \arrow[d, "g"] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55] \\
  & C_3 \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

 \begin{definition} An opposite category $\mathcal{C}^{op}$ is a category with all the same objects of category $\mathcal{C}$ and morphisms that are reversed. For example $f:C_1 \rightarrow C_2$ in $\mathcal{C}$ is $f:C_2 \rightarrow C_1$ in $\mathcal{C}^{op}$.   
 \end{definition}

@@

We model data as the sheaf $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op}\rightarrow \textcolor{section}{\bm{Set}}$. The objects of \textbf{Set} in this sheaf are the sets of sections introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps in \autoref{eq:related-work:continuity:presheaf}. 
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\textcolor{section}{\bm{Set}}) & \\
{} \arrow[rr, "\dfuncc", Rightarrow, pos=.3, shorten <=3.5em, shorten >=8.85em] & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{op}) \arrow[uu, "\sheafc(\dtotalc)", bend left, shift left = 10.5] \arrow[uu, "\sheafc(\dtotalc)"', bend right, shift left=10.5] &   
\end{tikzcd}
\end{equation}
The map $\dfunc: \sheaf(\dtotal) \rightarrow \sheaf(\dtotal)$ is any arbitrary morphism between sheaf functors $\sheaf(\dtotal)$. Following from \autoref{eq:related-work:equivariance:natural-transform}, \dfunc\ is a natural transform, which means all inclusions $\iota, \iota^*$ are preserved as part of any $\dfunc$ transformation.

@@

When a fiber bundle is trivial, we can dispense with localization and directly consider the fiber maps $Hom(\dfiber_{\dbasepoint}, \dfiber_{\dbasepoint})$ over a point \dbasepoint\ as the basis of our equivariance. This is because a sheaf $\sheaf(\dtotal)$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf(\dtotal)|_{\dbasepoint}\coloneqq \lim\limits_{\openset\ni \dbasepoint} \Gamma(\openset, \dtotal)$ \cite{StalkSheaf2019}. The fiber space over a point is embedded in the stalk over that point $\dfiber_{\dbasepoint}\hookrightarrow \mathscr{\dfiber}_{\dbasepoint}$. The sheaf maps \dfunc\ restricted to the stalk are members of $hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$. The maps $\dfunc \in Hom_{\mathcal{\dfiber}}(\dfiber,\dfiber)$ include the types of data transformations described in \autoref{sec:related-work:equivariance}In \autoref{sec:artist:construction}, we assume that the fiber bundles are trivial.

The continuity of the graphic is encapsulated as a category $\mathcal{\mathcal{\gbase}}$ containing open set objects $\opensetg$, the complete set of opensets $\gbase$ that is the full space of the graphic, and the empty set. As with $\mathcal{\dbase}$, the morphisms between the open sets  $\opensetg$ are inclusion morphisms $\iota$. Over the graphic space $\opensetg \subseteq \gbase$ are a set of sections 
\begin{equation}
  \label{eq:artist:graphic_sections}
  \cgamma{\opensetgc}{\gtotalc} \coloneqq \{\gsectionc^{i}:\opensetgc\rightarrow \gtotalc\}|_{i\in I}
\end{equation}
which are the set of all graphics with a shared base space and fiber and are a subcategory of \textbf{Set}. This allows us to represent the full space of graphics as a sheaf $\sheaf(\gtotal)$
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[row sep=huge]
    {Ob(\textcolor{section}{\bm{Set}}) \ni \cgamma{\opensetgc_i}{\gtotalc}}                                                                                                  &  & \{\gsectionc^{j}:\opensetgc_i\rightarrow \gtotalc\}|_{j\in J} \arrow[ll, "\iota"', hook'] \\ &  & \\
    \opensetgc_i \arrow[uu, "\sheafc(\gtotalc)"] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheaf_{\vartist}(\gtotalc)" description, dashed] &  & 
    \end{tikzcd}
\end{equation}
The set of graphics reachable through an artist function is a subset $\{\gsection^{j}\}|_{j\in J}$ of the full set of graphics. These sets of reachable graphics over open sets \opensetg\ are also objects of \textbf{Set}. This allows us to formulate the graphic output by the artist as a sheaf $\sheaf_{\vartist}$ from the graphic base space to the set of reachable graphics.

@@

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalc) \rightarrow \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set.
